Make_mash_U_hyp

### 2020-07-09 R/Make_mash_U_hyp.Rmd
Fix symmetry of U_dist U_hyp

  Ureturn <- list.append(Ureturn, U_wea = U_wea)
  names(Ureturn)[i] <- paste0("U_", str_extract(pattern[i], "[^$]+")) # matches one or more characters other than $
}
names(Ureturn)
Ureturn <- list.append(Ureturn, U_dist = U_dist)
```

@@

  Urow <- rep(Utest, each = 2)
  Utr <- matrix(unlist(Urow), nrow = nrow(Utest), ncol = ncol(Utest)*2)
  Ut <- rep(Utr, each = 2)
  Udup <- matrix(unlist(Ut), nrow = nrow(Utr)*2, ncol = ncol(Utr))
  colnames(Udup) <- rep(gulf_loc, each = 2)
  rownames(Udup) <- rep(gulf_loc, each = 2)
  Ugulf <- list.append(Ugulf, Udup = Udup)
  names(Ugulf)[i] <- names(Ureturn)[i]
}

write_rds(Ugulf, path = file.path(path, "U_hyp_gulf.rds"))
```

@@

gulf_loc <- c("CLMB", "KBSM", "KING", "PKLE", "TMPL")
midw_loc <- c("CLMB", "KBSM", "PKLE")
atl_loc <- c("CLMB", "KBSM", "LINC", "PKLE", "TMPL")
midwgulf_loc <- c("BRKG", "CLMB", "KBSM", "KING", "LINC", "PKLE", "STIL",
                  "TMPL")
U_gulf <- read_rds(file.path(path, "U_hyp_gulf.rds"))
i = 2
  m_out <- mash_standard_run(path = path, numSNPs = numSNPs[i], U_hyp = U_gulf,
                             suffix = paste0(phe_suffix[i], "_U_hyp_v1"),
                             saveoutput = TRUE)
```

>>>>

  Ureturn <- list.append(Ureturn, U_wea = U_wea)
  names(Ureturn)[i] <- paste0("U_", str_extract(pattern[i], "[^$]+")) # matches one or more characters other than $
}
names(Ureturn)

Ureturn$U_dist <- Ureturn$U_dist %>% as.data.frame()
Ureturn <- list.append(Ureturn, U_dist = U_dist)

str(Ureturn)
```

@@

  Urow <- rep(Utest, each = 2)
  Utr <- matrix(unlist(Urow), nrow = nrow(Utest), ncol = ncol(Utest)*2)
  Ut <- rep(Utr, each = 2)
  Udup <- matrix(unlist(Ut), nrow = nrow(Utr)*2, ncol = ncol(Utr))
  colnames(Udup) <- rep(gulf_loc, each = 2)
  rownames(Udup) <- rep(gulf_loc, each = 2)
  Ugulf <- list.append(Ugulf, Udup = Udup)
  names(Ugulf)[i] <- names(Ureturn)[i]
}
str(Ugulf)
write_rds(Ugulf, path = file.path(path, "U_hyp_gulf.rds"))

Ugulf$U_GR50
U_gulf_sym <- list()
isSymmetric(Ugulf$U_dist)
i = 2
for(i in seq_along(names(Ugulf))){
  Usym <- Ugulf[[i]]
  Usym1 <- Usym
  Usym2 <- Usym
  for(j in nrow(Usym1)){
    for(k in ncol(Usym1)){
      if(j < k){
        Usym1[j, k] <- Usym[j, k]
        Usym2[j, k] <- Usym[k, j]
      } else {
        Usym1[j, k] <- Usym[k, j]
        Usym2[j, k] <- Usym[j, k]
      }
    }
  }
  U_gulf_sym <- list.append(U_gulf_sym, U1 = Usym1, U2 = Usym2)
  length(names(U_gulf_sym))
  names(U_gulf_sym)[length(names(U_gulf_sym))-1] <- paste0(names(Ugulf)[i], "_1")
  names(U_gulf_sym)[length(names(U_gulf_sym))] <- paste0(names(Ugulf)[i], "_2")
}

write_rds(U_gulf_sym, path = file.path(path, "U_hyp_gulf_symmetric.rds"))

```

@@

gulf_loc <- c("CLMB", "KBSM", "KING", "PKLE", "TMPL")
midw_loc <- c("CLMB", "KBSM", "PKLE")
atl_loc <- c("CLMB", "KBSM", "LINC", "PKLE", "TMPL")
midwgulf_loc <- c("BRKG", "CLMB", "KBSM", "KING", "LINC", "PKLE", "STIL",
                  "TMPL")
U_gulf <- read_rds(file.path(path, "U_hyp_gulf_symmetric.rds"))
i = 2
  m_out <- mash_standard_run(path = path, numSNPs = numSNPs[i], U_hyp = U_gulf,
                             suffix = phe_suffix[i],
                             saveoutput = TRUE)
```
